### 2024-03-06 manuscript.tex
Added sentence referencing new hierarchy_mu figure in supporting.tex

\subsection{Clustering by evolutionary signatures reveals limited patterns of conserved features}
Given our observation of widespread signals of feature conservation in \textit{Drosophila} IDRs, we next sought to investigate if there are IDRs with similar patterns of conserved features and common functions. Accordingly, we treated the set of log likelihoods ratios for each region as its ``evolutionary signature'' and clustered them as in Zarin \textit{et al.}~\cite{Zarin2019}. The resulting heatmap reveals patterns of similar signatures interspersed among a high background of noise, and we identified at least 39 clusters with strong and consistent patterns of constraint (Fig~\ref{fig:hierarchy}). To gain greater insight into their functional properties, we performed term enrichment analyses using the annotations associated with each region's protein. After correcting for multiple comparisons using a 5\% false discovery rate, only five clusters were significantly enriched for any terms, which are given in Table~\ref{table:cluster_terms}. Most enriched terms are associated with fewer than ten proteins in each cluster, though the enriched terms for cluster 12 are markedly stronger and consistently associated with protein localization. We also observed that while many clusters are defined by a single strongly conserved feature, three (clusters 15, 23, and 24) have multiple features with signals of constraint. To determine if these more highly constrained regions are associated with a common underlying pattern of features, we compared their evolutionary signatures to normalized values of their inferred optima (Fig~\ref{fig:clusters}B-D). The heatmaps reveal that while the regions in these clusters have common patterns of constraint, the optimal values of their features can vary considerably. Likewise, cluster 12's strongly constrained feature, repeat\_K, is similarly variable (Fig~\ref{fig:clusters}A). Interestingly, this feature is consistent with its enrichment in annotations related to protein localization, as mitochondrial or nuclear targeting signals are characterized by a net positive charge or clusters of basic residues, respectively~\cite{Moulin2019, Lu2021}. However, the relative depletion of lysine repeats in some regions implies they are constrained against the formation of such targeting signals. This interpretation in turn suggests that IDRs may in general have complex relationships between their evolutionary constraints and functions where constraints can both preserve beneficial functions as well as prevent the acquisition of deleterious ones.

>>>>

\subsection{Clustering by evolutionary signatures reveals limited patterns of conserved features}
Given our observation of widespread signals of feature conservation in \textit{Drosophila} IDRs, we next sought to investigate if there are IDRs with similar patterns of conserved features and common functions. Accordingly, we treated the set of log likelihoods ratios for each region as its ``evolutionary signature'' and clustered them as in Zarin \textit{et al.}~\cite{Zarin2019}. The resulting heatmap reveals patterns of similar signatures interspersed among a high background of noise, and we identified at least 39 clusters with strong and consistent patterns of constraint (Fig~\ref{fig:hierarchy}). To gain greater insight into their functional properties, we performed term enrichment analyses using the annotations associated with each region's protein. After correcting for multiple comparisons using a 5\% false discovery rate, only five clusters were significantly enriched for any terms, which are given in Table~\ref{table:cluster_terms}. Most enriched terms are associated with fewer than ten proteins in each cluster, though the enriched terms for cluster 12 are markedly stronger and consistently associated with protein localization. We also observed that while many clusters are defined by a single strongly conserved feature, three (clusters 15, 23, and 24) have multiple features with signals of constraint. To determine if these more highly constrained regions are associated with a common underlying pattern of features, we compared their evolutionary signatures to normalized values of their inferred optima (Fig~\ref{fig:clusters}B-D). The heatmaps reveal that while the regions in these clusters have common patterns of constraint, the optimal values of their features can vary considerably. Likewise, cluster 12's strongly constrained feature, repeat\_K, is similarly variable (Fig~\ref{fig:clusters}A). Interestingly, this feature is consistent with its enrichment in annotations related to protein localization, as mitochondrial or nuclear targeting signals are characterized by a net positive charge or clusters of basic residues, respectively~\cite{Moulin2019, Lu2021}. However, the relative depletion of lysine repeats in some regions implies they are constrained against the formation of such targeting signals. This interpretation in turn suggests that IDRs may in general have complex relationships between their evolutionary constraints and functions where constraints can both preserve beneficial functions as well as prevent the acquisition of deleterious ones. Furthermore, though a similar analysis of the inferred optima reveals some analogous patterns of clusters, they are generally more fragmented and diffuse, indicating that despite these caveats, the log likelihood ratios can highlight common patterns of constraint that are not readily apparent from the optimal values of the molecular features alone (Fig~\ref{sfig:hierarchy_mu}).
